The \dealii{} Library, Version 9.2

### 2020-06-02 9.2/paper.tex
Fix python code indentation broken 9cd9120
fix large scale Stokes section, remove todo

As part of this effort, we ran benchmarks on the TACC Frontera system, where we were
able to apply the matrix-free geometric multigrid framework to a variable viscosity
Stokes system and achieved weak and strong scaling up to 114K MPI ranks with up to
\num{2.1e11} unknowns. This is likely the largest block system currently solved with
\dealii{} and required various optimizations
and fixes on top of the ones mentioned above:
(i) Bug fixes to concurrent point to point communications.
(ii) Fixes multigrid transfer with adaptive refinement and more than \num{4e9} unknowns.
(iii) Fixes to index sets in block indices with more than \num{4e9} unknowns.
(iv) Fixes to computations with more than \num{4e9} active cells.
(v) Implementation of IDR(s) solvers to reduce memory overhead.
For more details, see \cite{clevenger_stokes19}.

\todo[inline]{Timo added the paragraph above. Thoughts on how much we should mention (none of this worked with 9.1)?}

\todo[inline]{Martin: I think (ii) worked in 9.1/9.0/8.5, and (iv) definitely worked in the uniform case for 8.5, see Fig 1 in that paper, data line `8B cells'. We just happened to break things in between. But ``fixes'' is a good wording here because it doesn't exclude that some problems with those configurations have been solved before. So I like the text.}

@@

  for face in cell.faces():
  if face.at_boundary() and\
  face.boundary_id == 1:
  cell.refine_flag ='isotropic'

>>>>

As part of this effort, we ran benchmarks on the TACC Frontera system, where we were
able to apply the matrix-free geometric multigrid framework to a variable viscosity
Stokes system and achieved weak and strong scaling up to 114K MPI ranks with up to
\num{2.1e11} unknowns. This is likely the largest block system currently solved with
\dealii{} and required various optimizations
and fixes on top of the ones mentioned above:
(i) Bug fixes to concurrent point to point communications.
(ii) Fixes to multigrid transfer with adaptive refinement and more than \num{4e9} unknowns.
(iii) Fixes to index sets in block indices with more than \num{4e9} unknowns.
(iv) Fixes to computations with more than \num{4e9} active cells.
(v) Implementation of IDR(s) solvers to reduce memory overhead.
For more details, see \cite{clevenger_stokes19}.

@@

    for face in cell.faces():
        if face.at_boundary() and face.boundary_id == 1:
            cell.refine_flag = 'isotropic'
